{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-29 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

        Firstly, we will introduce some theories in for nonconvex functions. 
        This is necessary because Nesterov's monotone variants can adapt to weakly convex objective functions. 
        The following assumption will characterize the full scope of discussion in nonconvex objective function. 

@@

            \STATE{$z_1, p_0, \overline L_1:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

@@

                \IF{$M \le 0 \textbf{ or } G_k^+ \le \epsilon$}

@@

        So $x_{p_j}$ is assigned to $z_{j + 1}$ by the outer loop and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 

@@

            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$ and, $X^+$ is the set of minimizers. 

@@

            If in addition, $F$ satisfies the quadratic growth condition in Assumption \ref{ass:q-growth-ch2}, then 

@@

                \item [(f)] We used the monotone property of subroutine $\mathbf M$ in GMAPG again so $F(z_0) \le F(z_{j - 1})$. 
                \item [(g)] We substituted $T_\epsilon = \lceil\ln(2\epsilon^{-2}(F(z_0) - F^+))\rceil$ and, removing $\lceil\cdot\rceil$ to make for the $\le$ inequality. 

@@

            Finally, since the doubling must stop, Lemma \ref{lemma:rgmapg-outer-itr-bnd} applies hence, it terminates at most $j + T_\epsilon$ iteration. 

@@

            Using it let's assume that it executed for $j = 1, 2, \cdots, J$, and it can be represented as $J = m + nT_\epsilon$ with $0 \le m < T_\epsilon$. 

@@

                \item [(a)] 

@@

@@

        \begin{theorem}[convergence rates of restarted GMAPG]

>>>>

        The following definition is a set of necessary conditions GMAPG with Nesterov's monotone subroutine. 
        Our goal in this section is to show that Nesterov's implementations of monotone accelerated gradient method has convergence results under Assumption \ref{ass:sum-of-wcnvx}.

@@

            \STATE{$z_1, p_0, \overline L_1, G^+:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

                \IF{$M \le 0 \textbf{ or } G^+ \le \epsilon$}

@@

@@

        So $x_{p_j}$ is assigned to $z_{j + 1}$ by the outer loop, and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 

@@

            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$, $X^+$ is the set of minimizers, and $\mu > 0$ is the quadratic growth constant. 

@@

            Then it has

@@

                \item [(f)] We used the monotone property of subroutine $\mathbf M$ in GMAPG again so $F(z_0) \ge F(z_{j - 1})$. 
                \item [(g)] We substituted $T_\epsilon = \lceil\ln(2\epsilon^{-2}(F(z_0) - F^+))\rceil$ and, removing $\lceil\cdot\rceil$ to make for the $\le$ inequality. We also replaced $F(z_j)$ by $F^+$ the minimum which is always smaller. 

@@

            Finally, since the doubling must stop at some $j$, Lemma \ref{lemma:rgmapg-outer-itr-bnd} applies hence, it terminates at most $j + T_\epsilon$ iteration. 

@@

            Using it let's assume that it executed for $j = 1, 2, \cdots, J$ and $M$ is large enough to achieve optimality $G^+_k \le \epsilon$ right at the start of iteration $J$.
            Representing it by the maximum period between doubling: $J = m + nT_\epsilon$ with $0 \le m < T_\epsilon$. 

@@

                \item [(a)] $n_{J - lT_\epsilon} \le n_{J - lT_\epsilon}\le (1/2)^ln_J$ for all $l = 1, \ldots, n$. From Lemma \ref{lemma:rgmapg-outer-itr-bnd} we know that doubling must have occured within a period of $T_\epsilon$ iterations at least once.
                \item [(b)] $n_{j} \le n_{j + 1}$ for all $0 \le j \le J - 1$. The sequence is monotone from Observation \ref{obs:rgmapg}. 
                \item [(c)] $n_j \le \bar p$ with $\bar p = 4\sqrt{2L(1 + e)}/\sqrt{\mu}$, proved in Lemma \ref{lemma:rgmapg-inner-bnds}. 

@@

            The upper bound on the total number of iterations of GMAPG over $J$ iteration of outer loop is given by: 
                \sum_{i = 0}^{J} n_i &= \sum_{i = 0}^{m + nT_\epsilon} n_i
                &= \sum_{i = 0}^{m}n_i + \sum_{l = 0}^{n - 1}\sum_{i = 1}^{T_\epsilon} n_{m + i + lT}
                &\hspace{-0.5em}
                \underset{\substack{(b), \\ m \le T_\epsilon.}}\le T_\epsilon n_m + \sum_{l = 0}^{n - 1} T_\epsilon n_{m + (l + 1)T_\epsilon}
                &= T_\epsilon \sum_{l = 0}^{n} n_{m + lT_\epsilon} = T_\epsilon \sum_{l = 0}^{n} n_{J - lT_\epsilon}
                &\underset{\text{(a)}}{\le} T_\epsilon \sum_{l = 0}^{n} (1/2)^l n_J \le T_\epsilon \sum_{l = 0}^{\infty} (1/2)^l n_J
                &\le 2T_\epsilon n_J \le 2T_\epsilon \bar p.
            The total iteration counts is bounded by: 
                \sum_{i = 0}^{J} n_i &\le 
                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} \left\lfloor 
                \ln \left(

@@

        \begin{theorem}[convergence rates of restarted GMAPG]\label{thm:rgmapg-cnvg}
